CF Loop

### 2025-09-30 codes/R/CF_Loop.qmd
CF loop (reproducable)
Adjust for python settings

#--- python functions ---#
use_condaenv("cf_conda311", required = TRUE)
py_config()
py_run_string("from econml.dml import CausalForestDML; print('CausalForestDML imported OK')")

@@

## Data

```{r}
raw_sim_data <- readRDS(here::here("data/raw_sim_data.rds"))

# how many fields to train on?
n_fields <- 10

@@

      # Free ram 
      rm(res, te_hat_cf, te_info, response_data, train_data, test_data, e)
      if (i %% 10 == 0) gc()
    },
    error = function(e) {
      message("ERROR in sim ", test_sim_id, ": ", conditionMessage(e))
      err_row <- data.frame(
        test_sim_id = test_sim_id,
        error       = conditionMessage(e),
        ts          = as.character(Sys.time())
      )
      write.table(
        err_row,
        file      = file.path(output_dir, "errors.csv"),
        sep       = ",",
        row.names = FALSE,
        col.names = !file.exists(file.path(output_dir, "errors.csv")),
        append    = TRUE
      )
    }
  )
}

>>>>

#--- python functions ---#
use_condaenv("cf_conda311", required = TRUE)

# use_condaenv("cf_conda311",
#              conda = "/Users/monamousavi/miniforge3/bin/conda",
#              required = TRUE)

py_config()
py_run_string("from econml.dml import CausalForestDML; print('CausalForestDML imported OK')")

@@

## load data

```{r}
#raw_sim_data <- readRDS(here::here("data/raw_sim_data.rds"))

# how many fields to train on?
n_fields <- 20

@@

      # Free ram 
      rm(te_hat_cf, te_info, response_data, train_data, test_data, e)
      if (i %% 10 == 0) gc()
    },
    error = function(e) {
      message("ERROR in sim ", test_sim_id, ": ", conditionMessage(e))
      err_row <- data.frame(
        test_sim_id = test_sim_id,
        error       = conditionMessage(e),
        ts          = as.character(Sys.time())
      )
      write.table(
        err_row,
        file      = file.path(output_dir, "errors.csv"),
        sep       = ",",
        row.names = FALSE,
        col.names = !file.exists(file.path(output_dir, "errors.csv")),
        append    = TRUE
      )
    }
  )
}
